### 2025-06-30 sec/authoring-workflow.tex

\begin{itemize}
    \item \textbf{Interpreter Error}.
    Syntax errors due to incorrect use of the language (e.g., undeclared functions, invalid syntax, etc.).
    \item \textbf{String Error}.
    The expression does not return a string, violating the requirements of the \textit{System Prompt} (Fig.~\ref{fig:system-prompt}).
    \item \textbf{Value Mismatch}.
    If an expected value is known, it is compared with the actual result.
    The mismatch generates an error.
\end{itemize}

\subsection{Paragraph with generated expression}
\label{subsec:paragraph-with-generated-expression}
Figure \ref{fig:fluid-example-paragraph} shows the Fluid code of a Paragraph with Fluid expression generated by the authoring assistant.
Figure \ref{fig:fluid-scigen} shows the Fluid code written for the scigen datasets and examples.
\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid]{website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Fluid source code example Paragraph}
    \label{fig:fluid-example-paragraph}
\end{figure}

>>>>

\begin{itemize}
    \item \textbf{Invalid Program}.
    The generated expression is executed by the Fluid interpreter.
    If the execution fails due to issues such as undeclared functions, syntax errors, or other interpreter-level problems, it results in an \textit{Invalid Program} error.
    \item \textbf{Invalid Output Type}.
    According to the \textit{System Prompt} (Fig.~\ref{fig:system-prompt}), the expression is expected to return a string value.
    If the returned value is of a different type, an \textit{Invalid Output Type} error is raised.
    \item \textbf{Invalid Output Value}.
    The output produced by the generated expression is compared against the highlighted target text.
    If the values do not match, an \textit{Invalid Output Value} error is reported.
\end{itemize}

\subsection{Paragraph with generated expression}
\label{subsec:paragraph-with-generated-expression}
Figure \ref{fig:fluid-example-paragraph} shows the Fluid code of a Paragraph with the expression generated by the authoring assistant.
Figure \ref{fig:fluid-scigen} shows the Fluid code written for the scigen datasets and examples.
\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid]{website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Fluid source code example Paragraph}
    \label{fig:fluid-example-paragraph}
\end{figure}

### 2025-06-30 sec/evaluation.tex

\subsection{Success Rate by Testcase}
To evaluate the system we used a sample of the Scigen dataset \cite{scigen_dataset_2021}.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\linewidth]{fig/success_rate_by_category}
    \caption{Success rate by testcases}\label{fig:success_rate_by_category}
\end{figure}

>>>>

\subsection{Success Rate by Category}
To evaluate the system we used a sample of the Scigen dataset \cite{scigen_dataset_2021}.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.55\linewidth]{fig/success_rate_by_category}
    \caption{Success rate by testcases}\label{fig:success_rate_by_category}
\end{figure}

\subsection{Success Rate Category Count}

There are expressions which fall in more than one category.
Figure \ref{fig:success_rate_by_category_count} shows the results obtained in generating expression by the number of categories.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.55\linewidth]{fig/success_rate_by_category_count}
    \caption{Success rate by testcases}\label{fig:success_rate_by_category_count}
\end{figure}
